Quantum Interval-Valued Probability: Measurement and Probability

### 2017-09-27 prop_iop.tex
prop_iop.tex \subsection{Sates Consistent with a QIVPM Induced by the Born Rule} Updating...

\begin{lemma}Given a Hilbert space with the set of all projectors\nb$\events$,
and an interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
with the maximum length of intervals in $\mathscr{I}$ is $\delta$.
For two mixed state\nb$\rho$ and $\rho'$, if $\rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
then $\left\Vert \rho-\rho'\right\Vert \le\delta$.\end{lemma}

@@

The previous lemma can be applied on example~\ref{ex:equilateral},
we can estimate the states consistent with a QIVPM more tightly.

@@

Previously, we proved that if $\rho'$ is consistent with $\iota\circ\mu_{\rho}^{\mathrm{B}}$,
then $\rho'$ is close to $\rho$. However, if $\rho'$ is close to
$\rho$, there is no way to guarantee $\rho'$ is consistent with
$\iota\circ\mu_{\rho}^{\mathrm{B}}$ because no matter how close between
two real numbers~$x$ and $y$, we can never guarantee $y\in\iota\left(x\right)$.

>>>>

\begin{lemma}Given a Hilbert space with the set of all projectors\nb$\events$,
and an additive interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
with the maximum length of intervals in $\mathscr{I}$ is $\delta$.
For two mixed states\nb$\rho$ and $\rho'$, if $\rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
then $\left\Vert \rho-\rho'\right\Vert \le\delta$.\end{lemma}

@@

By applying the previous lemma on example~\ref{ex:equilateral},
we can estimate the states consistent with a QIVPM more tightly.

@@

Previously, we proved that if $\rho'$ is consistent with $\iota\circ\mu_{\rho}^{\mathrm{B}}$,
then $\rho'$ is close to $\rho$. However, if $\rho'$ is close to
$\rho$, there is no way to guarantee $\rho'$ is consistent with
$\iota\circ\mu_{\rho}^{\mathrm{B}}$ because no matter how close between
two real numbers~$x$ and $y$, we can never guarantee $y\in\iota\left(x\right)$
as in the following example.

\begin{example}Given an additive interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$,
consider let $x_{0}=\sup\set{x\in\left[0,1\right]}{\iota\left(x\right)=\left[0,0\right]}$.
Since $\iota\left(1\right)=\left[1,1\right]$, $x_{0}<1$. For any
$\varepsilon>0$, $\left|\left(x+\frac{\varepsilon}{2}\right)-x\right|=\frac{\varepsilon}{2}<\varepsilon$,
and $x+\frac{\varepsilon}{2}\ge\frac{\varepsilon}{2}>0$ implies $x+\frac{\varepsilon}{2}\notin\left[0,0\right]=\iota\left(x\right)$.

Notice that even if we explicitly exclude $0$ and $1$, the previous
argument applies on any boundary points among intervals. Therefore,
there is no way to avoid this problem if we have more than three intervals.\end{example}
